---
title: "index"
author: "Evan Odell"
date: "sys.Date()"
output:
  html_document:
    toc: true
---

# Documentation

Online documentation for my R packages.

## Packages:

### [`hansard`](https://docs.evanodell.com/hansard)

[![license](https://img.shields.io/github/license/mashape/apistatus.svg)]() 
[![CRAN\_Status\_Badge](https://www.r-pkg.org/badges/version/hansard)](https://cran.r-project.org/package=hansard) 
[![GitHub tag](https://img.shields.io/github/tag/evanodell/hansard.svg)](https://github.com/evanodell/hansard)
[![](https://cranlogs.r-pkg.org/badges/grand-total/hansard)](https://dgrtwo.shinyapps.io/cranview/)
[![DOI](https://zenodo.org/badge/72111315.svg)](https://zenodo.org/badge/latestdoi/72111315)

An ironically named R package to automatically fetch data from the UK Parliament API. Available on [CRAN](https://cran.r-project.org/package=hansard) and [GitHub](https://github.com/EvanOdell/hansard). `hansard` is part of the [rOpenGov](https://ropengov.github.io/) project and its documentation is mirrored on the [rOpenGov website](https://ropengov.github.io/hansard/).

### [`mnis`](https://docs.evanodell.com/mnis)

[![license](https://img.shields.io/github/license/mashape/apistatus.svg)](https://github.com/EvanOdell/mnis/blob/master/LICENSE)
[![CRAN\_Status\_Badge](https://www.r-pkg.org/badges/version/mnis)](https://cran.r-project.org/package=mnis)
[![GitHub tag](https://img.shields.io/github/tag/evanodell/mnis.svg)](https://github.com/evanodell/mnis)
[![](https://cranlogs.r-pkg.org/badges/grand-total/mnis)](https://dgrtwo.shinyapps.io/cranview/)
[![DOI](https://zenodo.org/badge/76553907.svg)](https://zenodo.org/badge/latestdoi/76553907)

An R package for downloading data from the Members' Names Information Service API operated by the UK Parliament. Available on [CRAN](https://cran.r-project.org/package=mnis) and [GitHub](https://github.com/EvanOdell/mnis).

### [`parlitools`](https://docs.evanodell.com/parlitools)

[![license](https://img.shields.io/github/license/mashape/apistatus.svg)](https://github.com/EvanOdell/parlitools/blob/master/LICENSE)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/parlitools)](https://cran.r-project.org/package=parlitools)
[![GitHub tag](https://img.shields.io/github/tag/evanodell/parlitools.svg)](https://github.com/evanodell/parlitools)
[![](https://cranlogs.r-pkg.org/badges/grand-total/parlitools)](https://dgrtwo.shinyapps.io/cranview/)
[![DOI](https://zenodo.org/badge/86801920.svg)](https://zenodo.org/badge/latestdoi/86801920)

A collection of tools, datasets and maps for analysing UK politics. Available on [CRAN](https://cran.r-project.org/package=parlitools) and [GitHub](https://github.com/EvanOdell/parlitools). Use [`parlitools`](https://docs.evanodell.com/parlitools) to create maps like this: 

```{r map, echo=FALSE, fig.height=6, message=FALSE, warning=FALSE}
library(leaflet)
library(sf)
library(htmlwidgets)
library(dplyr)
library(hansard)
library(mnis)
library(parlitools)

west_hex_map <- parlitools::west_hex_map

party_colour <- parlitools::party_colour

mps <- mps_on_date()

mps_colours <- left_join(mps, party_colour, by = "party_id") #Join to current MP data

west_hex_map <- left_join(west_hex_map, mps_colours, by = "gss_code") #Join colours to hexagon map

# Creating map labels
labels <- paste0(
  "<strong>", west_hex_map$constituency_name, "</strong>", "</br>",
  "Party: ", west_hex_map$party_name, "</br>",
  "MP: ", west_hex_map$display_as, "</br>",
  "Most Recent Result: ", west_hex_map$result_of_election, "</br>",
  "Current Majority: ", west_hex_map$majority, " votes"
) %>% lapply(htmltools::HTML)

# Creating the map itself
leaflet(options=leafletOptions(
  dragging = FALSE, zoomControl = FALSE, tap = FALSE,
  minZoom = 6, maxZoom = 6, maxBounds = list(list(2.5,-7.75),list(58.25,50.0)),
  attributionControl = FALSE),
  west_hex_map) %>%
  addPolygons(
    color = "grey",
    weight=0.75,
    opacity = 0.5,
    fillOpacity = 1,
    fillColor = ~party_colour,
    label=labels)  %>% 
  htmlwidgets::onRender(
    "function(x, y) {
        var myMap = this;
        myMap._container.style['background'] = '#fff';
    }")
```

### [`nomisr`](https://docs.evanodell.com/nomisr)

[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://opensource.org/licenses/MIT)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/nomisr)](https://cran.r-project.org/package=nomisr)
[![GitHub tag](https://img.shields.io/github/tag/evanodell/nomisr.svg)](https://github.com/evanodell/nomisr)
[![](https://cranlogs.r-pkg.org/badges/grand-total/nomisr)](https://dgrtwo.shinyapps.io/cranview/)
[![Travis-CI Build Status](https://travis-ci.org/evanodell/nomisr.svg?branch=master)](https://travis-ci.org/evanodell/nomisr)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/evanodell/nomisr?branch=master&svg=true)](https://ci.appveyor.com/project/evanodell/nomisr)
[![Coverage Status](https://img.shields.io/codecov/c/github/evanodell/nomisr/master.svg)](https://codecov.io/github/evanodell/nomisr?branch=master)
[![DOI](https://zenodo.org/badge/118144805.svg)](https://zenodo.org/badge/latestdoi/118144805)

`nomisr` is for accessing [Nomis](https://www.nomisweb.co.uk/) data -- UK labour market statistics, census data and other populatlion data -- with R.

## Installation

You can install nomisr from github with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("evanodell/nomisr")
```



### [`emisc`](https://docs.evanodell.com/emisc)

[![license](https://img.shields.io/github/license/mashape/apistatus.svg)](https://github.com/EvanOdell/emisc/blob/master/LICENSE)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/emisc)](https://cran.r-project.org/package=emisc)
[![GitHub tag](https://img.shields.io/github/tag/evanodell/emisc.svg)](https://github.com/evanodell/emisc)
[![](https://cranlogs.r-pkg.org/badges/grand-total/emisc)](https://dgrtwo.shinyapps.io/cranview/)
[![DOI](https://zenodo.org/badge/96876145.svg)](https://zenodo.org/badge/latestdoi/96876145)

`emisc` is a collection of miscellaneous functions that I have made that may or may not be useful, and that may or may not duplicate existing work.

`emisc` is currently not available on CRAN. You can install `emisc` from github with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("evanodell/emisc")
```





